---
title: "tables"
author: "Upul Cooray"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y at %H:%M')`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

This analysis was conducted to assess different opinions regarding the introduction of RFID (denture identification system)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(labelled)
library(gtsummary)
library(flextable)

# import data

load("data/isudata.RData")


```

```{r include=FALSE}

data <- df %>%  mutate(Speciality= case_when(Speciality== "forensic odontologist"~ "Forensic odontologists/ Carer",
                                             Speciality== "Carer"~ "Forensic odontologists/ Carer",
                                             TRUE~ "Other related proffession") %>% as.factor(),
                       
                       `Widely introduce RFID`= if_else(`Introduce RFID`== "Widely introduce","Agree","Not agree") %>% as_factor(),
                       `Against RFID`= if_else(`Introduce RFID`== "Aginst RFID","Against", "Not against") %>% as_factor()) 

```

<!-- ==============================Define table function====================== -->

```{r tab-fun, include=FALSE}

 

tab.fun <- function(staff="",headvar, full= FALSE) {
  
  
  
  if (full) {
    data.den <- data %>% select(headvar, `Introduce RFID`,`Widely introduce RFID`, `Against RFID` ) 
    staff <- "all participants"
  } 
  
  else {
    data.den <-      data %>% filter(`Staff type`== staff) %>% 
      select(headvar,`Introduce RFID`, `Widely introduce RFID`, `Against RFID` )  
    staff <- paste(staff,"staff")
  } 
  
    
  
  header <- data.den %>% select(all_of(headvar)) %>% colnames()
  
  title <- paste("Opinion on RFID introduction among",tolower(staff), "based on",tolower(header))
  
 tbl_summary(data.den,by= headvar)  %>%  
    
    add_p() %>% 
    modify_caption(caption = title) %>% 
    modify_spanning_header(c("stat_1", "stat_2") ~ header) %>% 
    bold_labels() %>% 
    modify_header(update = all_stat_cols() ~ "{level}\nN = {n}",) %>%
    as_flex_table() %>% 
    compose(i=2,j=1, part='header', value = as_paragraph("Opinion"))
  
}

forensic_num <- (data %>%  filter(`Staff type`=="Dental") %>% .$Speciality %>%  table())[[1]]
carer_num <- (data %>%  filter(`Staff type`=="Nursing") %>% .$Speciality %>%  table())[[1]]

```


## *Difference in opinion among professionals based on work experience*

```{r    message=FALSE}

tab.fun("Dental","Work experience")
tab.fun("Nursing","Work experience")
tab.fun(headvar = "Work experience", full = TRUE )

```

## *Difference in opinion based on the specialty*

```{r    message=FALSE}
tab.fun("Dental","Speciality") %>%  
  compose(i=2, j = "stat_1",
          value = as_paragraph("Forensic odontologists\n N= ",
                               as_chunk({forensic_num})),
          part = "header") %>% 

tab.fun("Nursing","Speciality") %>%  
  compose(i=2, j = "stat_1",
          value = as_paragraph("Carers\n N= ",
                               as_chunk({forensic_num})),
          part = "header") %>% 
  

tab.fun(headvar = "Speciality", full = T)
  
```

## *Difference in opinion based experience on other systems*

```{r  message=FALSE}

tab.fun("Dental","Seen other") 
tab.fun("Nursing","Seen other") 
tab.fun(headvar = "Seen other", full = T) 


```

## *Difference in opinion based prior knowledge on RFID*

```{r  message=FALSE}

tab.fun("Dental","Know RFID") 
tab.fun("Nursing","Know RFID")
tab.fun(headvar = "Know RFID", full = TRUE)

```

## *Difference in opinion based prior knowledge on RFID*

```{r}

# tab.fun("Dental","Seen RFID") 
# tab.fun("Nursing","Seen RFID")
# tab.fun(headvar = "Seen RFID", full = TRUE)

```


## *Difference in opinion based prior knowledge on RFID*

```{r  message=FALSE}

tab.fun("Dental","Heard of IMP")
tab.fun("Nursing","Heard of IMP")
tab.fun(headvar = "Heard of IMP", full = TRUE)

```



